PS753 Glossary

### 2022-01-30 _academics/ps753-glossary/ps753-glossary.Rmd
Test of bibtex citation

---
title: "PS753 Glossary"
description: |
  Glossary page for PS753 coursework
author:
  - name: Steve Linberg
    url: {}
date: 2022-01-29
output:
 distill::distill_article:
   self_contained: false
---

@@

node / vertex
: a junction in a network where two or more lines (edges) intersect; a dot connecting lines.<br>

edge / link
: lines connecting nodes, which indicate some sort of connection or relationship.

node or ego
: $i$ - the node being discussed or focused on

@@

snowball sample
: an entity group formed by starting with one node and "rolling outwards" to its connections until all nodes or actors (in a limited set) are located

@@

>>>>

---
title: "PS753 Glossary"
description: |
  Glossary page for PS753 coursework
author:
  - name: Steve Linberg
    url: {}
date: 2022-01-29
output:
 distill::distill_article:
   self_contained: false
bibliography: PS753.bib
---

@@

(Note: some terms overlap somewhat or have context-dependent synonyms.)

node / vertex
: a junction in a network where two or more lines (edges) intersect; a dot connecting lines.

tie / edge / link
: lines connecting nodes, which indicate some sort of connection or relationship.

node / ego / actor
: $i$ - the node being discussed or focused on

@@

snowball sample
: an entity group formed by starting with "a focal actor or set of actors"^[@hanneman] and "rolling outwards" to its connections until all nodes or actors (in a limited set) are located

@@

---

https://retorque.re/zotero-better-bibtex/
